Medical Concept Extraction

### 2012-12-14 paper/paper.tex
Adding the parameter selection figure.
Adding work on the system section.

@@

Discuss and cite LIBSVM, LIBLINEAR and CRFSUITE.

@@

Where we can see the system running live.

>>>>

\begin{figure}
\begin{center}
	\includegraphics[width=1\columnwidth]{figures/parameter-selection.png}
\end{center}
\caption{An illustration of the grid search process to identify the best parameters values for training the SVM model.}
\label{fig:parameter_selection}
\end{figure}

@@

All of the code is available online at the following url:

{\tt https://github.com/tnaumann/ConceptExtraction}.

\subsubsection{Commandline Utilities}

@@

In addition to the various command line utilizes described in the previous section our system also includes a Web-based service that allows users to manually input a single sentence, select a model to use for prediction, and see the predicted labels that model generated for the input. Figure~\ref{fig:web_interface} shows a screenshot of the Web interface in use.

The Web service was written in Python and directly interoperates with the rest of the code base. To run the Web applications simply execute the {\tt web.py} file in the source tree. The Web app assumes that models have already been trained and placed into ``models'' directory in the source tree. By default, the application will host itself on port 5000. You can also see a live version of the Web service at:

{\tt http://saahmad.media.mit.edu:5000/ }

\begin{figure}
\begin{center}
	\includegraphics[width=1\columnwidth]{figures/web-interface.png}
\end{center}
\caption{The Web application interface that allows users to manually input a sentence and have it labeled using one of the previously-trained models. In this case we are using an SVM model that was trained using all of the features.}
\label{fig:web_interface}
\end{figure}

\subsection{Libraries}

Our code leveraged various 3rd party libraries for training the models and generating features. A summary of the libraries that we used is shown in the list below:

\item {\tt libsvm} \cite{libsvm}: libsvm provides a fast implementation of Support Vector Machines. It includes a command line utility that takes a training data (with all of the features formatted in a sparse matrix representation) as input and outputs a SVM model trained on that data. It also includes a command line utility that allows users to specify a desired model and predict the classes on new input. Our code base forks process calls to these utilities to train SVM models, although a lot of the parameter tuning and feature selection is handled elsewhere in our codebase.

\item {\tt liblinear} \cite{liblinear}: lib linear is a linear classifier library that has special support multi-class classification. It also provides easy to use training and predicting command line utilities that accept a similar input format as libsvm.

\item {\tt crfsuite} \cite{crfsuite}: crfsuite is an implementation for conditional random fields and includes command line front ends to train a model on data and to predict the labels on an unseen data set. The data format for the input training files is also a sparse matrix representation but is slightly different from the format used by libsvm and lib linear. Our codebase nicely abstracts out these format differences and produces the right format depending on the model in use.

\item {\tt nltk} \cite{nltk}: nltk is a very popular NLP library written in Python. We leverage nltk to generate some of the features on our data. In particular, we utilize nltk's maximum-entropy part-of-speech tagging as well as many of its stemming algorithms.

\item {\tt flask} \cite{flask}: Flask is a micro Web framework written in Python. It contains a small yet useful set of features that allow developers to easily setup RESTful Web backends and an elegant tempting system to gracefully generate HTML. Flask is used to build the Web service portion of the project.
